---
title: "flat_calculate_land_use_frac.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

```{r}
library(terra)
library(dplyr)
library(targets)
library(here)

tar_load(land_use, branches = 1:2, store = here("_targets"))
```

# calculate_land_use_frac

Now, let's surmise that we had multiple types:

```{r}
land_type_1 <- land_use$land_use_90929f80e69014c8
land_type_2 <- land_use$land_use_d5272583bc0e6381
plot(land_type_1)
plot(land_type_2)
```

How would we know the proportion of the country covered by each
type? First, we need to merge (concatenate) the two rasters together 
with `merge()`:

```{r}
merged <- merge(land_type_1, land_type_2)
plot(merged)
```

Then, we need an aggregation object to calculate
the proportion of the country covered by each type.

To do this, we can fetch the healthsheds for madagascar:

```{r}
hlthshed <- tar_read(mdg_healthshed, store = here("_targets")) %>%
  read_sf()
```

This is a `SpatRaster` with two layers, one for grass and one for trees.

Now, we can calculate the proportion of the country covered by each type:

```{r}

```

```{r development-calculate_land_use_frac}
# Prepare the code of your function here
```

```{r function-calculate_land_use_frac}
#' calculate_land_use_frac Title
#'
#' @return 1
#' @export
#'
#' @examples
calculate_land_use_frac <- function() {
  1
}
```

```{r examples-calculate_land_use_frac}
calculate_land_use_frac()
```

```{r tests-calculate_land_use_frac}
test_that("calculate_land_use_frac works", {
  expect_true(inherits(calculate_land_use_frac, "function"))
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_calculate_land_use_frac.Rmd", vignette_name = "Go further")
```

