---
title: "flat_download_landcover_geodata.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Downloading Land Cover with the `geodata` Package

Fortunately, most of the work of interacting with the ESA WorldCover API is handled by the `geodata` package. 
This package provides a convenient interface for downloading and processing geospatial data from
the ESA WorldCover API, including land cover datasets.

```{r}
library(geodata)
```

Using this library is very straightforward — you just provide the
type of land cover you want, and an output dir:

```{r}
landcover_trees <- landcover("trees", path = tempdir())
landcover_trees
```

Clearly this will need a bounding box, since the API
just fetches data for all the globe. To do this,
we can reference `graydon`'s bounding boxes in the
`country-bounding-boxes` package, which we have included as a dependency in our `conda` environment.
We source this function with `reticulate` to get the bounding box for Madagascar:

```{r}
library(reticulate)
library(cli)
library(dplyr)
library(purrr)
library(here)
```

```{r}
reticulate::use_condaenv("/n/home03/ttapera/.local/share/mamba/envs/landuse", required = TRUE)
source_python(here("inst/py/get_bounding_box_for_iso_code.py"))
x <- get_bounding_box_for_iso_code_py("MDG")
box <- x$bbox
box
```

Great, so that is how we will get the bounding box. We
can wrap that in a function:
    
```{r development-get_bounding_box_for_iso_code}
# You can prepare the code of the get_bounding_box_for_iso_code() function here
```
  
```{r function-get_bounding_box_for_iso_code}
#' Get a country bounding box from an ISO3 code
#'
#' Calls a Python helper through `reticulate` to retrieve the bounding box for
#' a country identified by its ISO3 code. The function attempts to activate the
#' requested conda environment, sources the Python file, and returns the
#' bounding box as a named list.
#' 
#' @importFrom reticulate use_condaenv source_python
#' @importFrom cli cli_alert_danger cli_alert_info
#' @importFrom purrr flatten
#'
#' @param iso_code Character scalar giving the ISO3 country code, for example
#'   `"NPL"`.
#' @param python_file Character scalar giving the path to the Python script that
#'   defines `get_bounding_box_for_iso_code_py()`.
#' @param reticulate_python_env Character scalar giving the name of the conda
#'   environment to use with `reticulate`.
#'
#' @return A named list with four elements: `xmin`, `ymin`, `xmax`, and `ymax`.
#'
#' @export
#'
#' @examples
#' \dontrun{
#' get_bounding_box_for_iso_code("NPL")
#' }
get_bounding_box_for_iso_code <- function(
  iso_code = "NPL", 
  python_file = system.file("py/get_bounding_box_for_iso_code.py", package = "LandUsePLN"),
  reticulate_python_env = "/n/home03/ttapera/.local/share/mamba/envs/landuse"
  ){

    # set up reticulate to use the correct python environment
    tryCatch({
      use_condaenv(reticulate_python_env, required = TRUE)
    }, error = function(e) {
      cli_alert_danger("Error finding Python environment: {e$message}. The function may not be able to run without the correct Python environment set up.")
    })

    # source the python function
    source_python(python_file)

    bbox <- get_bounding_box_for_iso_code_py(iso_code)
    cli_alert_info("Python return result for {iso_code}: {bbox}")

    bounding_box <- list(
      xmin = bbox$bbox[1],
      ymin = bbox$bbox[2],
      xmax = bbox$bbox[3],
      ymax = bbox$bbox[4]
    ) %>%
      flatten()
    return(bounding_box)

}
```
  
```{r example-get_bounding_box_for_iso_code}
get_bounding_box_for_iso_code("NPL")
```
  
```{r tests-get_bounding_box_for_iso_code}
test_that("get_bounding_box_for_iso_code works", {
  expect_true(inherits(get_bounding_box_for_iso_code, "function")) 
})
```

How does it get used to get a portion of the land use slice?
In the `terra` package, this is done by cropping the `ext`
of the raster:

```{r}
plot(landcover_trees)
```

```{r}
# xmin, xmax, ymin, ymax
ext(landcover_trees)
```

So, to crop the raster, we can simply do:

```{r}
npl_box <- get_bounding_box_for_iso_code("NPL")
cropper <- rast()
xmin(cropper) <- npl_box$xmin
xmax(cropper) <- npl_box$xmax
ymin(cropper) <- npl_box$ymin
ymax(cropper) <- npl_box$ymax
landcover_npl <- crop(landcover_trees, cropper)
plot(landcover_npl)
```

Beautiful! A tiny function to wrap this up will make it modular:
    
```{r development-crop_landcover_with_box}
# You can prepare the code of the crop_landcover_with_box() function here
```
  
```{r function-crop_landcover_with_box}
#' Crop a landcover raster with a bounding box
#' 
#' This function takes a landcover raster and a bounding box, and crops the raster to the extent of the bounding box. It also has an option to plot the cropped raster.
#' 
#' @importFrom terra rast xmin xmax ymin ymax crop plot
#' 
#' @param landcover_raster A `SpatRaster` object representing the landcover data to be cropped.
#' @param bounding_box A named list with four elements: `xmin`, `ymin`, `xmax`, `ymax`, representing the coordinates of the bounding box to crop to.
#' @param plot_invisible Logical scalar indicating whether to plot the cropped raster.
#' 
#' @return A `SpatRaster` object representing the cropped landcover data.
#' @export
crop_landcover_with_box <- function(landcover_raster, bounding_box, plot_invisible=FALSE) {
  
  cropper <- rast()
  xmin(cropper) <- bounding_box$xmin
  xmax(cropper) <- bounding_box$xmax
  ymin(cropper) <- bounding_box$ymin
  ymax(cropper) <- bounding_box$ymax
  cropped_landcover <- crop(landcover_raster, cropper)

  if(plot_invisible) {
    plot(cropped_landcover)
  }

  return(cropped_landcover)
    
}
```
  
```{r example-crop_landcover_with_box}
crop_landcover_with_box(landcover_raster = landcover_trees, bounding_box = get_bounding_box_for_iso_code("NPL"), plot_invisible = TRUE)
```
  
```{r tests-crop_landcover_with_box}
test_that("crop_landcover_with_box works", {
  expect_true(inherits(crop_landcover_with_box, "function")) 
})
```

This seems good. Now, we can wrap the above procedure in a single function
that downloads all of the landcover data for a given country:

```{r development-download_landcover_geodata}
# Prepare the code of your function here
```

```{r function-download_landcover_geodata}
#' Download and crop land cover data for a country
#'
#' Downloads a land cover raster for a specified cover type using
#' `geodata::landcover()`, retrieves the country's bounding box from its ISO3
#' code, and crops the raster to that extent.
#' 
#' @importFrom geodata landcover
#' @importFrom terra rast xmin xmax ymin ymax crop
#'
#' @param country_code Character scalar giving the ISO3 country code, for
#'   example `"NPL"`.
#' @param cover_type Character scalar giving the land cover type to download,
#'   for example `"trees"`.
#' @param tmp_path Character scalar giving the directory where the downloaded
#'   land cover file should be stored. Defaults to `tempdir()`.
#' @param plot_invisible Logical scalar passed to
#'   `crop_landcover_with_box()`. Controls whether the crop operation also
#'   produces a plot.
#'
#' @return A cropped land cover raster object returned by
#'   `crop_landcover_with_box()`.
#'
#' @export
#' @examples
#' \dontrun{
#' x <- download_landcover_geodata(country_code = "NPL", cover_type = "trees")
#' print(x)
#' }
download_landcover_geodata <- function(
  country_code = "NPL",
  cover_type = "trees",
  tmp_path = tempdir(),
  reticulate_python_env = "/n/home03/ttapera/.local/share/mamba/envs/landuse",
  plot_invisible = FALSE
  ) {
  
  # get the full tiff
  landcover_full <- landcover(cover_type, path = tmp_path)
  # get the bounding box for the country
  bounding_box <- get_bounding_box_for_iso_code(country_code, reticulate_python_env = reticulate_python_env)
  # crop the landcover to the bounding box
  landcover_cropped <- crop_landcover_with_box(landcover_full, bounding_box, plot_invisible = plot_invisible)

  return(landcover_cropped)
}
```

```{r examples-download_landcover_geodata}
download_landcover_geodata("NPL", "grassland")
```

```{r tests-download_landcover_geodata}
test_that("download_landcover_geodata works", {
  expect_true(inherits(download_landcover_geodata, "function"))
})
```

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_download_landcover_geodata.Rmd", vignette_name = "Downloading Land Cover with `geodata`", check=FALSE, open=FALSE, clean=TRUE)
```
