---
title: "flat_build_local_pipeline.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

## Preamble

The primary distribution mechanism of our data in the lab is via a
`targets` pipeline. `targets` is a powerful R package for
orchestrating data analysis pipelines. It helps manage dependencies,
ensures reproducibility, and optimizes performance by only rerunning
the parts of the pipeline that have changed.

In the lab, we separate the technical concerns of data storage, processing, analysis,
and reporting into distinct workspaces:

1. Storage: Each project's raw data is stored in a dedicated data repository on Google Drive (`Drive / <PROJECT> / 4. Datasets / <DATASET NAME>`).
  That dataset is _mirrored_ to FASRC via `rclone` for processing. To work on your
  own project, you must be on FASRC -- the pipeline will then _symlink_ the google drive data to your
  local "data/" directory using the `link_inputs()` function defined in the pipeline.
2. Processing and Analysis: The `targets` pipeline handles preliminary data processing
  and analysis. It reads raw data from the "data/" directory, processes it,
  and generates intermediate datasets and analysis results in your local workspace. To do this, simply:
    - Install this package in your local project space using `remotes::install_github()`.
    - Load the package using `library(your_package_name)`.
    - Run the `targets` pipeline by executing `tar_make()` in the R console. This will execute all defined targets, processing the data and generating clean datasets.
    - Access the processed data and analysis results stored in the `_targets/` directory using `tar_load()` or other `targets` functions.
3. Analysis: Once you've run the `targets` pipeline, you can access the processed data
  and analysis results stored in the `_targets/` directory. This data is then used
  for further analysis and reporting.
4. Reporting: Your modelling and analysis are conducted on your own in the project space,
  using the processed data outputs from the `targets` pipeline. You can create reports,
  visualizations, and other outputs based on the analysis results. I recommend using 
  Quarto for this purpose.
5. Sharing: Finally, when you are ready to share your work, use the respective project's
  Globus sharing endpoint or 
  `5. Data & Code Elements` Google Drive folder. This folder is intended for sharing
  intermediate data products — not raw or final data. You should always be able to reproduce
  any data product shared here by running the `targets` pipeline from raw data, and then rerunning
  your own analysis code.

# build_local_pipeline

This is a convenience function that can build the targets pipeline for the user
in their local project. It does this by providing skeleton code for the targets file,
as well as the list of necessary targets in a separate Quarto file, which is converted
to targets objects via `tarchetypes::tar_tangle()`

```{r development-libraries}
library(glue)
library(cli)
library(readr)
library(stringr)
library(dplyr)
library(fs)
library(here)
```

```{r development-build_local_pipeline}
# Prepare the code of your function here
```

```{r function-build_local_pipeline}
#' Build Targets Pipeline
#'
#' Dynamically build the targets pipeline for the project.
#' 
#' This function sets up the targets pipeline by defining a local `_targets.R` file
#' and using `tar_tangle()` to create the necessary targets from an Rmd file.
#' The Rmd file is, itself, this vignette — Pipeline Definition.
#' 
#' @importFrom here here
#' @importFrom fs file_copy file_exists
#' @importFrom cli cli_alert_success cli_alert_danger cli_alert_info cli_abort
#' @importFrom xfun gsub_file
#' @importFrom readr read_lines
#' @importFrom stringr str_subset
#' @return NULL
#' @export
build_local_pipeline <- function(
  targets_notebook_name = "_target_notebook.Rmd", 
  targets_file_name = "_targets.R", 
  pkg_name = "LandUsePLN", 
  vignette_name = "pipeline-definition.Rmd",
  overwrite = FALSE
  ) {
  
  # Define the path to the targets notebook definition and file
  targets_notebook <- here(targets_notebook_name)
  targets_file <- here(targets_file_name)

  # fetch this installed vignette
  vignette_path <- system.file(vignette_name, package = pkg_name)

  # assert that the vignette exists
  if (!file_exists(vignette_path)) {
    cli_alert_danger("Vignette '{vignette_name}' not found in package '{pkg_name}'.")
    cli_abort("Cannot proceed without the vignette file.")
  }

  # copy to local project
  file_copy(vignette_path, targets_notebook, overwrite = overwrite)
  # remove irrelevant quarto directives
  lines <- read_lines(targets_notebook) %>%
    str_subset("#\\| eval: no", negate = TRUE)
  writeLines(lines, targets_notebook)
  if(file_exists(targets_notebook)) {
    cli_alert_success("Created local targets notebook at: {targets_notebook}")
  } else {
    cli_abort("Failed to create targets notebook at: {targets_notebook}")
  }

  # fetch the installed template for _targets.R
  template_path <- system.file("_targets.R", package = pkg_name)

  # copy to local project
  file_copy(template_path, targets_file, overwrite = overwrite)
  cli_alert_success("Created local targets file at: {targets_file}")

  # replace the tar_tangle() default to use the local notebook name
  if(targets_notebook_name != "_target_notebook.Rmd") {
    
    gsub_file(
      targets_file,
      pattern = "_target_notebook.Rmd",
      replacement = targets_notebook_name
    )
    cli_alert_success("Updated targets file to use targets notebook: {targets_notebook_name}")
    
  }

  cli_alert_info("To build the base pipeline, run `targets::tar_make()` in your R console. Use `targets::tar_read()` or `targets::tar_load()` to access target outputs.")
  cli_alert_info("You can also edit the targets file to extend the pipeline as needed for your project.")

  return(invisible())
}
```

```{r examples-build_local_pipeline}
#build_local_pipeline()
```

```{r tests-build_local_pipeline}
test_that("build_local_pipeline works", {
  expect_true(inherits(build_local_pipeline, "function"))
})
```

# Pipeline Definition

Below we define the actual targets of the pipeline using `tar_tangle()`.

> Note: Because we are dealing with geospatial data,
we cannot define the entire pipeline in a single Rmd as
normal. Instead, we define the regular targets in this Rmd,
but for geospatial targets we define them in the targets file explicitly.

## Config

A YAML config file is used to define parameters for the pipeline. It is contained
within the package and then copied to the local project when `build_local_pipeline()` is run.

```{r, eval=FALSE}
#| format: file
#| packages: [fs, here, dplyr]

cfg_path <- system.file("config.yml", package = "LandUsePLN") %>%
  file_copy(here("config.yml"), overwrite = TRUE)
```

## Linking Inputs

As with all of our pipelines, we will need the `link_inputs()` function to symlink 
the raw data from the google drive mirror on FASRC to the local "data/" directory.
The GDrive date we're looking for is healthshed files, which we discuss in more detail below.

```{r}
#| format: file
#| packages: [here, purrr, cli]

input_files <- link_inputs(cfg_path = cfg_path)
```

## `geodata` Package & Other Additional Parameters

The main pipeline relies on the `geodata` package to download and
process the ESA WorldCover data. The parameters for the `geodata` 
functions are defined in the `cfg` above.

```{r, eval=FALSE}
#| packages: [config, tibble]
countries <- config::get("inputs", file = cfg_path)$countries
years <- config::get("inputs", file = cfg_path)$years

land_cover_types <- tribble(
  ~cover_type,  ~cover_description,         ~column,
  "trees",      "Tree Cover",               "10",
  "shrubs",     "Shrubland",                "20",
  "grassland",  "Grassland",                "30",
  "cropland",   "Cropland",                 "40",
  "built",      "Built-up Area",            "50",
  "bare",       "Bare / Sparse vegetation", "60",
  "snow",       "Snow and Ice",             "70",
  "water",      "Permanent Water Bodies",   "80",
  "wetland",    "Herbacious Wetland",       "90",
  "mangroves",  "Mangroves",                "95",
  "moss",       "Moss and Lichen",          "100"
)
```

```{r}
#| format: file
#| packages: [dplyr, stringr]
mdg_healthshed <- input_files %>%
  str_subset("healthsheds2022.shp$")

npl_healthshed <- input_files %>%
  str_subset("SHP_Final.shp$")
```

## Run `geodata` and Fetch Land Use .tiff Data

Next, we get the land use data for the specified countries and years using the `geodata` package.

```{r, eval=FALSE}

```

## Merge the .tiff Files

Importantly, we merge the .tiff files into a single file per country-year. This used to
be done with the `gdal` library at the command line with the tool `gdal_merge.py`,
but that would necessitate going around the bend to install `gdal` on the local machine.
Instead, we install and make use of the `terra` package in R, which has superceded
`rgdal` for geospatial data processing in R and keeps our pipeline language-opinionated and contained.

```{r, eval=FALSE}

```

## Get the Healthshed File(s)

Healthsheds are the catchment areas around health facilities. Most of our analyses
are conducted at the healthshed level, so we fetch the healthshed files from our GDrive store
on FASRC that we symlinked earlier.

```{r, eval=FALSE}

```

## Extract Land Use Data for Healthsheds

Finally, we extract the land use data for each healthshed polygon. This is the main output of the pipeline,
which you can then use for all of your downstream analyses.


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_build_local_pipeline.Rmd", vignette_name = "Pipeline Definition", check=FALSE, open=FALSE, clean=TRUE)
```

```{r development-copy, eval=FALSE}
# Also copy the pipeline-definition.Rmd to inst/
fs::file_copy("vignettes/pipeline-definition.Rmd", "inst/pipeline-definition.Rmd", overwrite = TRUE)
```
