---
title: "flat_download_landcover_geodata.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Downloading Land Cover with the `geodata` Package

Fortunately, most of the work of interacting with the ESA WorldCover API is handled by the `geodata` package. 
This package provides a convenient interface for downloading and processing geospatial data from
the ESA WorldCover API, including land cover datasets.

```{r}
library(geodata)
```

Using this library is very straightforward — you just provide the
type of land cover you want, and an output dir:

```{r}
landcover_trees <- landcover("trees", path = tempdir())
landcover_trees
```

Clearly this will need a bounding box, since the API
just fetches data for all the globe. To do this,
we can reference `graydon`'s bounding boxes in the
`country-bounding-boxes` package, which we have included as a dependency.
We source this function with `reticulate` to get the bounding box for Madagascar:

```{r}
library(reticulate)
```

```{r}
source_python("inst/get_bounding_box_for_iso_code.py")
x <- get_bounding_box_for_iso_code("MDG")
box <- x$bbox
box
```

Great, so that is how we will get the bounding box. How does it
get used to get a portion of the land use slice?

```{r}

```

```{r development-download_landcover_geodata}
# Prepare the code of your function here
```

```{r function-download_landcover_geodata}
#' download_landcover_geodata Title
#'
#' @return 1
#' @export
#'
#' @examples
download_landcover_geodata <- function() {
  1
}
```

```{r examples-download_landcover_geodata}
download_landcover_geodata()
```

```{r tests-download_landcover_geodata}
test_that("download_landcover_geodata works", {
  expect_true(inherits(download_landcover_geodata, "function"))
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_download_landcover_geodata.Rmd", vignette_name = "Go further")
```

