---
title: "flat_calculate_land_use_frac.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

```{r}
library(terra)
```

# calculate_land_use_frac

Now, let's surmise that we had multiple types:

```{r}
npl_grass <- download_landcover_geodata("NPL", "grassland", plot_invisible = TRUE)
npl_trees <- download_landcover_geodata("NPL", "trees", plot_invisible = TRUE)
```

How would we know the proportion of the country covered by each
type? First, we need to merge (concatenate) the two rasters together with the `c()` built-in (where
the value of each pixel is the land cover type, and there are multiple
dimensions of land cover type):

```{r}
grass_trees <- c(npl_grass, npl_trees)
grass_trees
```

This is a `SpatRaster` with two layers, one for grass and one for trees.

Now, we can calculate the proportion of the country covered by each type:

```{r}

```

```{r development-calculate_land_use_frac}
# Prepare the code of your function here
```

```{r function-calculate_land_use_frac}
#' calculate_land_use_frac Title
#'
#' @return 1
#' @export
#'
#' @examples
calculate_land_use_frac <- function() {
  1
}
```

```{r examples-calculate_land_use_frac}
calculate_land_use_frac()
```

```{r tests-calculate_land_use_frac}
test_that("calculate_land_use_frac works", {
  expect_true(inherits(calculate_land_use_frac, "function"))
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_calculate_land_use_frac.Rmd", vignette_name = "Go further")
```

